Bibliography

### 2016-11-23 Draft-1.tex
Changes from papeeria

    Church also defines boolean logic and operations used for them:

\begin{equation*}
\begin{aligned}
\bm{\mathrm{T}} &= \lambda ab.a,
  & % seperation
\bm{\mathrm{F}} &= \lambda ab.b
\end{aligned}
\end{equation*}
Note that for these functions which each takes two arguments, \textbf{T} outputs the first while \textbf{F} outputs the second. 
\end{document}

>>>>

    Church defines functions to operate boolean logic - firstly representing True and False:

\begin{equation*}
\begin{aligned}
\bm{\mathrm{T}} &= \lambda ab.a,
  & % seperation
\bm{\mathrm{F}} &= \lambda ab.b
\end{aligned}
\end{equation*}
These functions each take two arguments - the \textbf{T} function returns the first, while the \textbf{F} function returns the second. Functions representing boolean operations can also be defined:
\begin{gather*}
\begin{aligned}
\vee &= \lambda xy.x\bm{\mathrm{T}}y\\
\wedge &= \lambda xy.xy\bm{\mathrm{F}}\\
\lnot &= \lambda x.x\bm{\mathrm{FT}}
\end{aligned}
\end{gather*}
From these operations, the xor operation can be found
\begin{gather*}
\begin{aligned}
\oplus = \lambda xy.\wedge (\vee xy)(\lnot (\wedge xy))
\oplus = \lambda xy.x(\lnot y)y
\end{aligned}
\end{gather*}
\end{document}
